\section{Extensions and Cohomology of Groups}
\label{s:extensionsandcohomologyofgroups}
Let $G, B, \Pi$ be groups.
An exact sequence 
\begin{equation} 
\label{diag:groupextension} 
\begin{tikzcd}
E: 0 \arrow{r}& G \arrow{r}{\chi} & B \arrow{r}{\sigma} &\Pi \arrow{r}& 1
\end{tikzcd}
\end{equation}
is called a group extension of $G$ by $\Pi$.
For convenience $G,B$ are denoted as additive groups and $\Pi$ as a multiplicative group.
We define a homomorphism 
$\theta:B \to \Aut(G)$ 
via conjugation
\[
\chi (\theta(b)g) = b + \chi g - b 
\]
for $b\in B$ and $g\in G$.
Let $A:=G$ be an abelian group.
Then for any $b\in \ker \sigma$ by exactness $b=\chi a$ for some $a\in A$, hence $\theta(b) = 1_{A}$.
Therefore $\ker \sigma \subset \ker \theta$.
Thus we can define
$\phi : \Pi \to \ Aut(A)$ via the universal property of the quotient as the unique map such that $\phi\sigma = \theta$.
Call $\phi$ the operators of the extension $E$.
We have the following equality
\begin{equation}
\label{eq:operatorsphi}
\chi (\phi(\sigma(b))a) = b + \chi a - b
\end{equation}
for $a\in A$ and $b\in B$.
% Define Morphism $\Gamma: E \to E'$ via commutative diagram.
A morphism $\Gamma: E \to E'$ is a tuple of group homomorphisms $(\alpha,\beta,\gamma)$ such that the diagram
\begin{equation*}
%\label{diag:group_extension_morphism}
\begin{tikzcd}
E: \arrow{d}{\Gamma}&
A\arrow{r}\arrow{d}{\alpha}&
B \arrow{r}\arrow{d}{\beta}&
\Pi \arrow{d}{\gamma}
\\
E': &
A'\arrow{r} &
B'\arrow{r} &
\Pi'
\end{tikzcd}
\end{equation*}
commutes.
% Define congruence $E \equiv E'$ via morphism $(1_A,\beta,1_{\Pi})$
% Note that congruent extennsions have the same operators.
Two group extensions $E, E'$ are congruent if there is a morphism of the form $(1_A,\beta,1_{\Pi}):E \to E'$.
We use the familiar notation $E\equiv E'$ for congruent extensions.
As in the case of $\Ext{}$ we may speak of congruence classes of group extensions because $\beta$ is an isomorphism via the Short 5 Lemma.
\begin{lemma}
Congruent extensions have the same operators.
\end{lemma}
\begin{proof}
Consider extensions $E=(\chi,\sigma):A\to B\to \Pi$ with operators $\phi$ and $E'=(\chi',\sigma'):A\to B'\to \Pi$ with operators $\phi'$.
Assume $E$ and $E'$ are congruent, so there is a morphism $(1_A,\beta,1_{\Pi}):E \to E'$.
Let $b\in B$ and set $\sigma b = x$.
By commutativity $\sigma' \beta b = \sigma b = x$ and $\beta \chi = \chi'$.
By the definition of operators for $a\in A$ we have
\begin{align*}
\beta \chi (\phi(\sigma b)a) &= \beta b + \beta \chi a - \beta b \\
\Longrightarrow \; \beta \chi (\phi(x)a) &= \chi' (\phi'(\sigma' \beta b)a)\\
\Longrightarrow \;\;\, \chi' (\phi(x)a) &= \chi' (\phi'(x)a).
\end{align*}
Because $\chi'$ is injective the operators $\phi$ and $\phi'$ are equal.
\end{proof}
Denote the set of congruence classes of  group extensions of an abelian group $A$ by any group $\Pi$ with operators $\phi$ by $\Opext(\Pi,A,\phi)$.
\subsection{Group Ring}
In this subsection we follow \cite[Chapter 3.2.]{milies}.
Let $\Pi$ be any multiplicative group.
Let $\mathbb{Z}(\Pi)$ denote the set of all formal linear combinations
$\alpha = \sum_{x\in\Pi} a_x x$ where $a_x \in \mathbb{Z}$ with $a_x = 0$ for all but finitely many $x$.
We define the sum of two elements in $\mathbb{Z}(\Pi)$ by
\[
\left(\sum_{x\in\Pi} a_x x\right) + \left(\sum_{y\in\Pi} b_y y\right) = \sum_{x\in\Pi} (a_x + b_x) x.
\]
We define the product of two elements $\alpha=\sum_{x\in\Pi} a_x x$ and $\beta= \sum_{y\in\Pi} b_y y$ by
\[
\alpha\beta = \sum_{x,y\in\Pi} (a_x b_y) xy.
\]
These operations induce a ring structure on $\mathbb{Z}(\Pi)$.
A module over $\mathbb{Z}(\Pi)$ is called $\Pi$-module.
We want to show that a group homomorphism $\Pi\to Aut(A)$ for an abelian group $A$ defines a unique $\Pi$-module structure on $A$.

Define an embedding $\iota:\Pi \to \mathbb{Z}(\Pi)$ by $\iota(x)=1 \cdot x$.
Note that $\iota\Pi$ is a basis of $\mathbb{Z}(\Pi)$.

\begin{lemma}\cite[Proposition IV.1.1.]{maclane}
\label{lemma:universalproperty_groupring}
Let $\mu:\Pi \to R$ be a function with $\mu(1)=1$ and $\mu(xy)=\mu(x)\mu(y)$.
There is a unique ring homomorphism $\rho:\mathbb{Z}(\Pi)\to R$ such that the diagram
\[
\begin{tikzcd}
& \mathbb{Z}(\Pi) 
	\arrow{d}{\rho}
\\
\Pi 
	\arrow{ur}{\iota}
	\arrow{r}{\mu}
& R
\end{tikzcd}
\]
commutes.
\end{lemma}
\begin{proof}
Define $\rho(\sum_{x\in\Pi}a_x x):= \sum_{x\in\Pi}a_x \mu(x)$.
It is easy to check that this is a ring homomorphism and that the diagram commutes.
Since $\iota\Pi$ is a basis, $\rho$ is unique.
\end{proof}

\begin{lemma} \cite[Proposition IV.1.2.]{maclane}
Let $A$ be an abelian group.
A group homomorphism $\phi: \Pi \to Aut(A)$ gives $A$ a unique $\Pi$-module structure. 
\end{lemma}
\begin{proof}
The group homomorphisms $A \to A$ form a ring $End(A)$.
The automorphisms $Aut(A)$ are a subset of $End(A)$.
Extending the range of $\phi$ to $End(A)$ allows us to apply Lemma \ref{lemma:universalproperty_groupring}.
Hence $\phi$ induces a $\Pi$-module structure on $A$.
We say $A$ is a $\Pi$-module with operators $\phi$.
\end{proof}
%--------------------------
\input{ss_2_1}
\input{ss_2_2}